|

### 2023-03-06 paper_comparison/paper_comparison/paper_comparison.Rmd
fix the formula in the "what is being tested" section
After checking the packages and the original paper, I think it now looks closer to the correct form.

```{r}
# rewrite effect size here (if needed)

```

@@

However, it is practically impossible to test this specific $H_0$ with conventional tests, which are constructed to measure specific departures. For example, the RESET test is formulated as $H_0:\gamma_1 = \gamma_2 = \gamma_3 = 0$ against $H_a: \gamma_1 \neq 0 \text{ or } \gamma_2 \neq 0 \text{ or } \gamma_3 \neq 0$, from $e = \gamma_1\hat{y}^2 + \gamma_2\hat{y}^3 + \gamma_3\hat{y}^4 + u, ~~u \sim N(0, \sigma_u^2)$. 
Similarly, the BP test is designed to specifically test $H_0:$ *error variances are all equal* ($\tau=0$) versus the alternative $H_a:$ *that the error variances are a multiplicative function of one or more variables* ($\tau\neq 0$) from $e^2 = \tau\hat{y} + u, ~ u\sim N(0,\sigma_u^2)$.

>>>>

@@

However, it is practically impossible to test this specific $H_0$ with conventional tests, which are constructed to measure specific departures. For example, the RESET test is formulated as $H_0:\gamma_1 = \gamma_2 = \gamma_3 = 0$ against $H_a: \gamma_1 \neq 0 \text{ or } \gamma_2 \neq 0 \text{ or } \gamma_3 \neq 0$, from $e = \tau_0 + \tau_1x_1 + \cdots + \tau_1 x_p +\gamma_1\hat{y}^2 + \gamma_2\hat{y}^3 + \gamma_3\hat{y}^4 + u, ~~u \sim N(0, \sigma_u^2)$. 
Similarly, the Breusch-Pagan test is designed to specifically test $H_0:$ *error variances are all equal* ($\tau=0$) versus the alternative $H_a:$ *that the error variances are a multiplicative function of one or more variables* ($\tau\neq 0$) from $e^2 = \tau_0 + \tau_1 x_1 + \cdots + \tau_1 x_p + u, ~ u\sim N(0,\sigma_u^2)$.
